\section{Development}
So, for this project, we used the 2021 and 2017 Portuguese local elections as the basis.
The data was sourced from the official election results provided by the Portuguese government, which 
included detailed information on votes, candidacies, 
parties, and municipalities. We designed a database 
schema to efficiently store this data and implemented 
an ETL pipeline to extract, transform, and load the 
data into our database. 

\subsection{ETL Pipeline}

\subsection{Functions, Views, and Triggers}
All functions, views, and triggers were implemented in PostgreSQL using PL/pgSQL.
\begin{itemize}
    \item \textbf{Functions:}
    \begin{itemize}
        \item \texttt{calculate_vote_percentage(p_candidacy_id)}: Calculate vote percentage for a candidacy.
        \item \texttt{get_party_performance_in_municipality(p_election_id, p_municipality_id,
        p_party_acronym)}: Get the performance of a party in a specific municipality.
        \item \texttt{get_top_parties(p_election_id, p_municipality_id, 
        p_organ_id, p_limit)}: Get the top parties in a specific municipality.
        \item \texttt{allocate_seats_dhondt(p_election_id, p_organ_id, 
        p_municipality_id, p_total_seats)}: Allocate seats based on the D'Hondt method for a specific election and municipality.
        \item \texttt{calculate_turnout_percentage()}: Calculate voter turnout percentage.
        \item \texttt{get_or_create_party(p_party_acronym, p_party_name)}: 
        Get or create a party based on its acronym and name.
    \end{itemize}
    \item \textbf{Views:}
    \begin{itemize}
        \item \texttt{vw_complete_results}: A view that provides complete election results, including vote counts, percentages, and seat allocations for each candidacy.
        \item \texttt{vw_turnout_analysis}: A view that provides turnout analysis for each election and municipality.
        \item \texttt{vw_candidacy_details}: A view that provides complete candidacy information, including vote percentages and seat allocations.
        \item \texttt{vw_municipality_summary}: A view that summarizes election results by municipality, including total votes, turnout, and seat allocations.
        \item \texttt{vw_stg_missing_data}: A view that identifies any missing data in the staging tables, such as missing votes or candidacy information.
        \item \texttt{vw_stg_potential_duplicates}: A view that identifies potential duplicate records in the staging tables, such as duplicate votes or candidacies.
    \end{itemize}
    \item \textbf{Triggers:}
    \begin{itemize}
        \item \texttt{trg_turnout_percentages}: Automatically create turnout percentages on INSERT or UPDATE of votes.
        \item \texttt{trg_vote_percentages}: Automatically vote percentages on INSERT or UPDATE of votes.
        \item \texttt{trg_audit_log}: Audit log for important table changes (e.g., when a new election is added or when votes are updated).
        \item \texttt{trg_audit_candidacy}: Audit log for candidacy changes (e.g., when a new candidacy is added or updated).
        \item \texttt{trg_audit_vote_result}: Audit log for vote result changes (e.g., when votes are updated or when seat allocations are changed).
    \end{itemize}
\end{itemize}
\subsection{Analytical Queries}
After implementing the functions, views, and triggers,
 we tested them using SQL queries to ensure they were working 
 correctly and efficiently. We also analyzed the 
 results to gain insights into the election data, 
 such as identifying which parties had the most votes 
 and how the seats were allocated based on the D'Hondt method. \par 
 Here are some examples of the analytical queries we used to test our functions and views:
\begin{itemize}
    \item D'Hondt Seat Allocation:
    \begin{verbatim}

    \end{verbatim}
    \item Windows:
    \begin{itemize}
        \item 
    \end{itemize}
\end{itemize}

\subsection{Frontend Overview}
For the frontend, we used Flask to create a web application that allows users to interact with the election data.
The frontend provides a user-friendly interface to query the database and visualize the results, 
such as displaying vote percentages and seat allocations in a more intuitive way. 
\par In it, we 
\subsection{Known Limitations}
\subsection{Short Statement of Individual Contributions}
\begin{itemize}
    \item \textbf{Amos Uwamusi:}
    \begin{itemize}
        \item Developed the ETL pipeline to extract, transform, and load the election data into the database.
        \item Implemented functions to calculate vote percentages and allocate seats based on the D'Hondt method.
        \item Created views to provide complete election results and turnout analysis.
        \item Developed triggers to automatically calculate percentages and maintain data integrity.
    \end{itemize}
    \item \textbf{Kamil Tasarz:}
    \begin{itemize}
        \item Designed and implemented the database schema to store the election data efficiently.
        \item Created functions to analyze party performance and get top parties in specific municipalities.
        \item Developed views to summarize election results by municipality and identify missing data.
    \end{itemize}
    \item \textbf{Sérgio Cardoso:}
    \begin{itemize}
        \item Adapted the data handling processes to manage multiple elections and municipalities, ensuring scalability and flexibility.
        \item Developed both the report and the slides for the presentation, summarizing the project and its outcomes effectively.
    \end{itemize}
\end{itemize}